% !TEX root = ../main.tex
% =====================================================================
%  00-cover.tex -- cover page, disclaimer, how-to-use, table of contents
% =====================================================================

% --- COVER ----------------------------------------------------------
\begin{titlepage}
  \rcfeCover
  \vspace{18pt}

  \SectionAccent{rcfeNavy}{rcfeGoldSoft}
  \begin{rcfecallout}[title={How to Use This Cheat Sheet}]
  \footnotesize
  \begin{description}[leftmargin=5.6em,labelwidth=5em,labelsep=0.5em,itemsep=2pt,topsep=2pt]
    \item[Section 1] Master Timeline -- every time-based deadline.
    \item[Section 2] Critical Values -- temperatures, dimensions, ratios.
    \item[Section 3] SHALL vs.\ MAY -- 15+ high-risk wording traps.
    \item[Section 4] Red Flag / Penalty -- prohibited acts \& dollar fines.
    \item[Section 5] Citation Index -- alphabetical jump table.
  \end{description}
  \end{rcfecallout}

  \vspace{10pt}
  \SectionAccent{rcfeCrimson}{rcfeCrimsonSoft}
  \begin{rcfecallout}[title={Mandatory Disclaimer}]
  \footnotesize
  This reference excerpts only language explicitly stated in the
  California Code of Regulations, Title~22, Division~6, Chapter~8 and
  the California Health \& Safety Code §1569 series. Where Title~22 and
  the H\&S Code differ, both are noted and the stricter requirement is
  flagged. Every entry includes its specific section citation. Always
  verify against the current published code before relying on any item
  for licensing, enforcement, or examination purposes. This product is
  a study aid; it is not legal advice and is not affiliated with the
  California Department of Social Services or the Community Care
  Licensing Division.
  \end{rcfecallout}
\end{titlepage}

% --- TABLE OF CONTENTS ---------------------------------------------
\SectionAccent{rcfeNavy}{rcfeGoldSoft}
\begingroup
\renewcommand{\baselinestretch}{1.15}\normalsize
\tableofcontents
\endgroup
\clearpage

% --- LEGEND ---------------------------------------------------------
\SectionAccent{rcfeNavy}{rcfeGoldSoft}
{\sffamily\Large\bfseries\color{rcfeNavy} Legend \& Citation Key}\par\vspace{2pt}
\noindent{\color{rcfeNavy}\rule{\linewidth}{1pt}}\par\vspace{8pt}

\footnotesize
\begin{cheattable}{>{\raggedright\arraybackslash}p{0.30\linewidth} >{\raggedright\arraybackslash}p{0.66\linewidth}}{Symbol}{Meaning}
\tr{\TT{XXXXX}}{California Code of Regulations, Title~22, §XXXXX}
\tr{\HS{1569.xx}}{Health \& Safety Code, §1569.xx}
\tr{\BOTH{T22}{HS}}{Both citations apply; stricter governs}
\tr{\shall}{Mandatory action; no discretion}
\tr{\may}{Permissive action; discretion allowed}
\tr{\shallnot}{Absolute prohibition}
\tr{LIC \#}{Licensing Form Number (CDSS/CCLD)}
\tr{DCS}{Direct Care Staff}
\tr{POC}{Plan of Correction}
\tr{POO}{Plan of Operation}
\end{cheattable}
\clearpage
